---
title: "Fish Catches"
author: "Vanessa Murakami"
date: "11/14/2019"
output:
  html_document: default
  pdf_document: default
---

## Fish Catches
What is going to be looked at will be if certain species of fish are being caught depending on year and country.

##Required Packages

```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
```

## Looking at all catches in 22 countries for 2006, 2010, and 2014

These years were picked because it will look at the first, middle, and last years collected.

```{r}
all_data<-read.csv("Raw_Data/fish_catches.csv")
head(all_data)
```

**Calculating sums for each country for the years 2006, 2010, and 2014 **


```{r}
data_long<-all_data %>%
  gather(year, fish_counts,X2014:X2013:X2012:X2011:X2010:X2009:X2008:X2007:X2006)

```



```{r,cache.comments=FALSE}
#Belgium catches
BE<-filter(all_data,Country=="BE")
sum(BE[,5])
sum(BE[,9])
sum(BE[,13])

#Germany catches
DE<-filter(all_data,Country=="DE")
sum(DE[,5])
sum(DE[,9])
sum(DE[,13])

#Denmark catches
DK<-filter(all_data,Country=="DK")
sum(DK[,5])
sum(DK[,9])
sum(DK[,13])

#Estonia catches
EE<-filter(all_data,Country=="EE")
sum(EE[,5])
sum(EE[,9])
sum(EE[,13])

#Spain catches
ES<-filter(all_data,Country=="ES")
sum(ES[,5])
sum(ES[,9])
sum(ES[,13])

#Finland catches
FI<-filter(all_data,Country=="FI")
sum(FI[,5])
sum(FI[,9])
sum(FI[,13])

#Faroe Islands catches
FO<-filter(all_data,Country=="FO")
sum(FO[,5])
sum(FO[,9])
sum(FO[,13])

#France Catches
FR<-filter(all_data,Country=="FR")
sum(FR[,5])
sum(FR[,9])
sum(FR[,13])

#UK (Chanel Island Guersney) catches
GG<-filter(all_data,Country=="GG")
sum(GG[,5])
sum(GG[,9])
sum(GG[,13])

#Greenland catches
GL<-filter(all_data,Country=="GL")
sum(GL[,5])
sum(GL[,9])
sum(GL[,13])

#Ireland catches
IE<-filter(all_data,Country=="IE")
sum(IE[,5])
sum(IE[,9])
sum(IE[,13])

#UK (Isle of Man) catches
IM<-filter(all_data,Country=="IM")
sum(IM[,5])
sum(IM[,9])
sum(IM[,13])

#UK (Channel Island Jersey) Catches
JE<-filter(all_data,Country=="JE")
sum(JE[,5])
sum(JE[,9])
sum(JE[,13])

#Lithuania catches
LT<-filter(all_data,Country=="LT")
sum(LT[,5])
sum(LT[,9])
sum(BE[,13])

#Latvia catches
LV<-filter(all_data,Country=="LV")
sum(LV[,5])
sum(LV[,9])
sum(LV[,13])

#Netherlands catches
NL<-filter(all_data,Country=="NL")
sum(NL[,5])
sum(NL[,9])
sum(NL[,13])

#Norway catches
NO<-filter(all_data,Country=="NO")
sum(NO[,5])
sum(NO[,9])
sum(NO[,13])

#Poland catches
PL<-filter(all_data,Country=="PL")
sum(PL[,5])
sum(PL[,9])
sum(PL[,13])

#Portugal catches
PT<-filter(all_data,Country=="PT")
sum(PT[,5])
sum(PT[,9])
sum(PT[,13])

#Russia catches
RU<-filter(all_data,Country=="RU")
sum(RU[,5])
sum(RU[,9])
sum(RU[,13])

#Sweden catches
SE<-filter(all_data,Country=="SE")
sum(SE[,5])
sum(SE[,9])
sum(SE[,13])

#United Kingdom catches
UK<-filter(all_data,Country=="UK")
sum(UK[,5])
sum(UK[,9])
sum(UK[,13])


```
Get rid of the countries that didn't have any catch for all three years looked at.

## Histogram for catch for 22 countires in years 2006, 2010, and 2014

Data frame of the file "Clean_Data/Total_catch.csv" was created using excel spreadsheet and transfered to a csv to be looked at in R.

```{r}
total_catch<-read.csv("Clean_Data/Total_catch.csv")
head(total_catch)
data<-gather(total_catch,key, value, -Country)
head(data)
ggplot(data, aes(key,value))+
  geom_bar(aes(fill=Country),stat="identity",position="dodge")+
  labs(x="Year")
ggsave("Figures/Country_Catches_Histogram.jpg")

```


## Belgium Fish Catches from 2006-2014

```{r}
fish_catch<-read.csv("Clean_Data/BelgiumCatch.csv")
head(fish_catch)
```

** Calculating sums for each year **

```{r,message=FALSE}
fourteen<-sum(fish_catch[,3])
fourteen
thirteen<-sum(fish_catch[,4])
thirteen
twelve<-sum(fish_catch[,5])
twelve
eleven<-sum(fish_catch[,6])
eleven
ten<-sum(fish_catch[,7])
ten
nine<-sum(fish_catch[,8])
nine
eight<-sum(fish_catch[,9])
eight
seven<-sum(fish_catch[,10])
seven
six<-sum(fish_catch[,11])
six
```



Data frame of fish caught in each year:

```{r}
by_year <- matrix(c(2014, 79514,
                2013, 76153,
                2012, 73134,
                2011, 66582,
                 2010, 65723,
                 2009, 63634,
                2008, 66298, 
              2007, 72089,
                2006, 67564), byrow=T, nrow=9, ncol=2)
by_year
colnames(by_year)<-c("Year", "Number_of_Fish")
by_year
catch_per_year<-data.frame(by_year)
catch_per_year

```



## Scatter Plot of fish caught from each year

```{r}
ggplot(catch_per_year)+
  geom_point(aes(Year,Number_of_Fish))
ggsave("Figures/Belgium_Catches_per_Year_scatter.jpg")

```




