---
title: "Fish Catches"
author: "Vanessa Murakami"
date: "11/14/2019"
output:
  html_document: default
  pdf_document: default
---

## Fish Catches
What is going to be looked at will be if certain species of fish are being caught depending on year and country.

##Required Packages

```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
```

## Looking at all catches in 22 countries for 2006, 2010, and 2014

These years were picked because it will look at the first, middle, and last years collected.

```{r}
all_data<-read.csv("Raw_Data/fish_catches.csv")
head(all_data)
```

**Calculating sums for each country for the years 2006, 2010, and 2014 **


```{r}
data_long<-all_data %>%
  gather(year, fish_counts,X2014:X2013:X2012:X2011:X2010:X2009:X2008:X2007:X2006)
data_long

```

```{r}
total<- all_data %>%
  select(Species, Country,X2014,X2010,X2006 )%>%
  gather(year, count, X2014:X2010:X2006)
total_caught<-data.frame(total)
```


```{r,cache.comments=FALSE}
#Belgium catches
BE<-filter(all_data,Country=="BE")
sum(BE[,5])
sum(BE[,9])
sum(BE[,13])

#Germany catches
DE<-filter(all_data,Country=="DE")
sum(DE[,5])
sum(DE[,9])
sum(DE[,13])

#Denmark catches
DK<-filter(all_data,Country=="DK")
sum(DK[,5])
sum(DK[,9])
sum(DK[,13])

#Estonia catches
EE<-filter(all_data,Country=="EE")
sum(EE[,5])
sum(EE[,9])
sum(EE[,13])

#Spain catches
ES<-filter(all_data,Country=="ES")
sum(ES[,5])
sum(ES[,9])
sum(ES[,13])

#Finland catches
FI<-filter(all_data,Country=="FI")
sum(FI[,5])
sum(FI[,9])
sum(FI[,13])

#Faroe Islands catches
FO<-filter(all_data,Country=="FO")
sum(FO[,5])
sum(FO[,9])
sum(FO[,13])

#France Catches
FR<-filter(all_data,Country=="FR")
sum(FR[,5])
sum(FR[,9])
sum(FR[,13])

#UK (Chanel Island Guersney) catches
GG<-filter(all_data,Country=="GG")
sum(GG[,5])
sum(GG[,9])
sum(GG[,13])

#Greenland catches
GL<-filter(all_data,Country=="GL")
sum(GL[,5])
sum(GL[,9])
sum(GL[,13])

#Ireland catches
IE<-filter(all_data,Country=="IE")
sum(IE[,5])
sum(IE[,9])
sum(IE[,13])

#UK (Isle of Man) catches
IM<-filter(all_data,Country=="IM")
sum(IM[,5])
sum(IM[,9])
sum(IM[,13])

#UK (Channel Island Jersey) Catches
JE<-filter(all_data,Country=="JE")
sum(JE[,5])
sum(JE[,9])
sum(JE[,13])

#Lithuania catches
LT<-filter(all_data,Country=="LT")
sum(LT[,5])
sum(LT[,9])
sum(BE[,13])

#Latvia catches
LV<-filter(all_data,Country=="LV")
sum(LV[,5])
sum(LV[,9])
sum(LV[,13])

#Netherlands catches
NL<-filter(all_data,Country=="NL")
sum(NL[,5])
sum(NL[,9])
sum(NL[,13])

#Norway catches
NO<-filter(all_data,Country=="NO")
sum(NO[,5])
sum(NO[,9])
sum(NO[,13])

#Poland catches
PL<-filter(all_data,Country=="PL")
sum(PL[,5])
sum(PL[,9])
sum(PL[,13])

#Portugal catches
PT<-filter(all_data,Country=="PT")
sum(PT[,5])
sum(PT[,9])
sum(PT[,13])

#Russia catches
RU<-filter(all_data,Country=="RU")
sum(RU[,5])
sum(RU[,9])
sum(RU[,13])

#Sweden catches
SE<-filter(all_data,Country=="SE")
sum(SE[,5])
sum(SE[,9])
sum(SE[,13])

#United Kingdom catches
UK<-filter(all_data,Country=="UK")
sum(UK[,5])
sum(UK[,9])
sum(UK[,13])


```
Get rid of the countries that didn't have any catch for all three years looked at.

## Histogram for catch for 22 countires in years 2006, 2010, and 2014

Data frame of the file "Clean_Data/Total_catch.csv" was created using excel spreadsheet and transfered to a csv to be looked at in R.

```{r}
total_catch<-read.csv("Clean_Data/Total_catch.csv")
head(total_catch)
total_catch_long<-gather(total_catch,year, counts, -Country)
head(total_catch_long)
ggplot(total_catch_long, aes(year,counts))+
  geom_bar(aes(fill=Country),stat="identity",position="dodge")+
  labs(x="Year")
ggsave("Figures/Country_Catches_Histogram.jpg")

```


## Belgium Fish Catches from 2006-2014

```{r}
fish_catch<-read.csv("Clean_Data/BelgiumCatch.csv")
head(fish_catch)
```



```{r}
BEdata<- fish_catch %>%
  gather(year, count, X2014:X2013:X2012:X2011:X2010:X2009:X2008:X2007:X2006)
BEdataframe<-data.frame(BEdata)
head(BEdataframe)
write.csv(BEdataframe,"Clean_data/BE_total_catch.csv")
BE_catch<-BEdata%>%
  select(year,count)
head(BE_catch)
new_BE<-BE_catch%>%
  group_by(year)%>%
  summarize(count=sum(count))
new_BE
```




```{r}
ggplot(new_BE)+
  geom_point(aes(year,count))+
  labs(y="total count")
ggsave("Figures/Belgium_Catches_per_Year_scatter.jpg")
```

Looking at total count per species caught in 2006-2014

```{r}
BE_Species<-BEdataframe%>%
  group_by(Species)%>%
  summarise(count=sum(count))
BE_Species
```

```{r}
NO<-all_data%>%
  filter(Country=="NO")%>%
  select(X2014,X2013,X2012,X2011,X2010,X2009,X2008,X2007,X2006)
NO
longNO<-gather(NO)
sum(NO$X2014)
NO_by_year<-matrix(c(2014, sum(NO$X2014),
       2013, sum(NO$X2013),
       2012, sum(NO$X2012),
       2011, sum(NO$X2011),
       2010, sum(NO$X2010),
       2009, sum(NO$X2009),
       2008, sum(NO$X2008),
       2007, sum(NO$X2007),
       2006, sum(NO$X2006)), nrow=9, ncol=2,byrow=TRUE) 
colnames(NO_by_year)<-c("year","count")
NO_by_year
NO_data<-data.frame(NO_by_year)
ggplot(NO_data)+
  geom_point(aes(year,count))+
  labs(y="total count")


```


SE Fish Catches

```{r}
SE<-all_data%>%
  filter(Country=="SE")%>%
  select(X2014,X2013,X2012,X2011,X2010,X2009,X2008,X2007,X2006)
SE
longSE<-gather(SE)
sum(SE$X2014)
SE_by_year<-matrix(c(2014, sum(SE$X2014),
       2013, sum(SE$X2013),
       2012, sum(SE$X2012),
       2011, sum(SE$X2011),
       2010, sum(SE$X2010),
       2009, sum(SE$X2009),
       2008, sum(SE$X2008),
       2007, sum(SE$X2007),
       2006, sum(SE$X2006)), nrow=9, ncol=2,byrow=TRUE) 
colnames(SE_by_year)<-c("year","count")
SE_by_year
SE_data<-data.frame(SE_by_year)
ggplot(SE_data)+
  geom_point(aes(year,count))+
  labs(y="total count")


```


RU Fish Catches

```{r}
RU<-all_data%>%
  filter(Country=="RU")%>%
  select(X2014,X2013,X2012,X2011,X2010,X2009,X2008,X2007,X2006)
RU
longRU<-gather(RU)
sum(RU$X2014)
RU_by_year<-matrix(c(2014, sum(RU$X2014),
       2013, sum(RU$X2013),
       2012, sum(RU$X2012),
       2011, sum(RU$X2011),
       2010, sum(RU$X2010),
       2009, sum(RU$X2009),
       2008, sum(RU$X2008),
       2007, sum(RU$X2007),
       2006, sum(RU$X2006)), nrow=9, ncol=2,byrow=TRUE) 
colnames(RU_by_year)<-c("year","count")
RU_by_year
RU_data<-data.frame(RU_by_year)
ggplot(RU_data)+
  geom_point(aes(year,count))+
  labs(y="total count")


```


UK Fish Catches

```{r}
UK<-all_data%>%
  filter(Country=="UK")%>%
  select(X2014,X2013,X2012,X2011,X2010,X2009,X2008,X2007,X2006)
NO
longUK<-gather(UK)
sum(UK$X2014)
UK_by_year<-matrix(c(2014, sum(UK$X2014),
       2013, sum(UK$X2013),
       2012, sum(UK$X2012),
       2011, sum(UK$X2011),
       2010, sum(UK$X2010),
       2009, sum(UK$X2009),
       2008, sum(UK$X2008),
       2007, sum(UK$X2007),
       2006, sum(UK$X2006)), nrow=9, ncol=2,byrow=TRUE) 
colnames(UK_by_year)<-c("year","count")
UK_by_year
UK_data<-data.frame(UK_by_year)
ggplot(UK_data)+
  geom_point(aes(year,count))+
  labs(y="total count")


```
